### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	14:50:32	(Tue18.Mar)

We would like to thank the associate editor for his efforts and for his speedy replies to queries from the authors, and reviewers for their thorough and highly relevant comments. A summary of our answers are provided below, and subsequent sections will target each reviewer's comments in detail. We quote in \textbf{bold face} statements from the reviewers, and provide our replies in ordinary print,

\section{Summary of response to reviewer's comments}

\newpage
\section{Answer to reviewer 1}

>>>>

We would like to thank the associate editor for his efforts and for his speedy replies to queries from the authors, and reviewers for their thorough and highly relevant comments. Subsequent sections will target each reviewer's comments in detail. We quote in \textit{italic} statements from the reviewers, and provide our replies in ordinary print,

\section{Answer to reviewer 1}
